ShrinkNets: Learning Network Size while Training

### 2018-02-09 paper/ICML/approach.tex

In this section we describe the \shrink approach, which allows us to learn
the network size as part of the training process. The key idea is the addition
of \swls after each layer in the network;  these layers
allow us to selectively deactivate neurons during training.  We start by introducing the
basic method, and then explain how to adapt the training procedure to support this new
layer.

>>>>

In this section we describe the \shrink approach. We discuss first the new \swls
which are used to deactivate neurons, followed by a description of how we adapt
the training loss function.

%In this section we describe the \shrink approach, which allows us to learn
%the network size as part of the training process. The key idea is the addition
%of \swls after each layer in the network;  these layers
%allow us to selectively deactivate neurons during training.  We start by introducing the
%basic method, and then explain how to adapt the training procedure to support this new
%layer.
